Change in Mobility and Site Occupation during the Late Pleistocene in Korea

### 2019-12-04 analysis/paper/paper.Rmd
working on the newer intro with three quesetions. I want to paraphrase the questions with more details and make connection to actual analyses. I feel nervous about writing with no Grammerly :/

@@

k_kas_sites_sheets <- map(p_sheets, ~path %>% )

>>>>

<!-- this is what I'm newly writing 
In this research, we try to answer the three questions to understand the technological transition period. First, we are asking how did the introduction of the new tools change the usage of landscape. The new technology might allow hunter-gatherers to explore and stay in different or harsher territories by increasing mobility as well as innovating hunting strategies []. Or people could change their landscape using the new tools such as [].

Second, we focus on how did the new technology change the way people use their sites whether they tended to stay in one spot longer as a base campe or shorter period for specific purpose such as summer hunting camp. The stone artifact assemblages from a site indicates how long a group stayed or what they did so we can assume the way people use the site []. This project will look into stone assemblages that hunter-gatherers left behind to understand the site occupation pattern change during the transition period.

Lastly, 
and the population dynamics.

--->

@@

#k_kas_sites_sheets <- map(p_sheets, ~path %>% )

#simply combine the two data sets of general info and assemblage info?
#kk_sheets <- c (mydata, kasa)
